Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increase Repair Time?

### 2015-03-13 data.tex
upgraded pickture of Royce case study

\sei{One paragraph summary on the key points of TSP execution? The following text should also be reviewed and better integrated.}
TSP guiding principles include 1) engineering work does not happen by accident, it must be planned, 2) the plans must include realistic commitments of the resources needed to perform the work, 3) planed and actual results should be frequently examined to assure that plans remain relevant, and 4) people performing the work should be responsible for planning and tracking the work. After clarifying goals, defining work practices, and estimating size and effort, developers make a detailed short term plan. As the developers perform project work, they use a tool such as the Process Dashboard to collect their time, effort, size, and schedule data. Every week, the team review their data to evaluate status, review actual rates, determine if project goals for schedule, cost, and quality are being met and then make necessary plan corrections. At the end of the project the coach and team perform a quantitative post mortem.

>>>>

\sei{One paragraph summary on the key points of TSP execution? The following text should also be reviewed and better integrated.}

TSP guiding principles include 1) engineering work does not happen by accident, it must be planned, 2) the plans must include realistic commitments of the resources needed to perform the work, 3) planed and actual results should be frequently examined to assure that plans remain relevant, and 4) people performing the work should be responsible for planning and tracking the work. After clarifying goals, defining work practices, and estimating size and effort, developers make a detailed short term plan. As the developers perform project work, they use a tool such as the Process Dashboard to collect their time, effort, size, and schedule data. Every week, the team review their data to evaluate status, review actual rates, determine if project goals for schedule, cost, and quality are being met and then make necessary plan corrections. At the end of the project the coach and team perform a quantitative post mortem.
